---
title: "Processing Eurobarometer 80.2"
author: "Daniel Antal, CFA"
date: "4/27/2020"
output: 
  github_document:
    toc: true
  html_document:
    toc: true
    theme: united
---

## Setup The Eurobarometer Package

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

list_of_packages <- installed.packages()
if ( ! "eurobarometer" %in% list_of_packages ) {
  devtools::install_github('antaldaniel/eurobarometer')
}

library(eurobarometer)
library(tidyverse)
```

## Read In Data 

You can read in the SPSS file with `haven`, which is part of `tidyverse`. 

```{r readeb13, eval=FALSE}
# Change to eval=TRUE if you want to run this code
ZA5877_raw <- haven::read_spss(file.path("not_included", "ZA5877_v2-0-0.sav"))
```

You can analyze the SPSS file with `gesis_metadata_create`.

```{r metadata, eval=FALSE}
# Change to eval=TRUE if you want to run this code
ZA5877_metadata <- gesis_metadata_create(dat = ZA5877_raw)

ZA5877 <- ZA5877_raw %>%
  purrr::set_names ( as.character(ZA5877_metadata$canonical_name)) %>%
  mutate ( region_nuts_names  = sjlabelled::as_label(region_nuts_codes)
           ) %>%
  mutate ( region_nuts_codes =  as.character(sjlabelled::as_labelled(region_nuts_codes)
           ))
```

### Preprocessing the Eurobarometer 80.2 Data

```{r preprocess13, eval=FALSE}
source(file.path("R", "which_coal_region.R"))
# Change to eval=TRUE if you want to run this code
eb13 <- ZA5877 %>%
  select ( one_of("serious_world_problems_climate_change",
                  "serious_world_problems_climate_change_sum" ,
                  "climate_change_action_generate_renewable_energy",
                  "gvrnmnt_targets_for_renewable_energy_importance",
                  "region_nuts_names", "region_nuts_codes",
                  "age_exact", "age_education", "type_of_community",
                  "age_education_5_cat_recoded",
                  "country_code_iso_3166"),
           contains("occupation")) %>%
  mutate_at( vars(starts_with("serious"),
                  starts_with("climate")), recode_mentioned) %>%
  mutate_at ( vars(starts_with("type"),
                   contains("recoded"),
                   contains("occupation")), haven::as_factor) %>%
  mutate ( government_targets = haven::as_factor(gvrnmnt_targets_for_renewable_energy_importance)) %>%
  mutate ( government_targets_numeric =  case_when (
           grepl("Not very|Not at all", 
                 as.character(government_targets)) ~ 0,
           grepl("Fairly|Very", as.character(government_targets)) ~ 1,
           government_targets == "DK" ~ NA_real_,
           TRUE ~ NA_real_ )
           ) %>%
  mutate ( age_education = recode_age_education(var = age_education,
                                                age_exact = age_exact )
           ) %>%
  mutate  ( is_rural = case_when (
    grepl ( "rural", tolower(as.character(type_of_community))) ~ 1,
    grepl ( "town", tolower(as.character(type_of_community)))  ~ 0,
    TRUE ~ NA_real_)
) %>%
  mutate  ( is_student = case_when (
    grepl ( "studying", tolower(as.character(age_education_5_cat_recoded))) ~ 1,
    grepl ( "refuse", tolower(as.character(type_of_community)))  ~ NA_real_,
    TRUE ~ 0)
  ) %>%
  mutate ( year_survey = 2013 ) %>%
  mutate ( coal_region = which_coal_region(region_nuts_codes)) %>%
  mutate ( is_coal_region = ifelse (is.na(coal_region), 0, 1))

saveRDS(eb13, file.path("data", "eb13.rds"), 
        version = 2 )
```

I created a coal region proxy with this document: [Coal regions in transition](https://ec.europa.eu/energy/topics/oil-gas-and-coal/EU-coal-regions/coal-regions-transition_en)


## Simple Models 

### Simple GLM model outside Poland


```{r simplemodels}
eb13 <- readRDS(file.path("data", "eb13.rds"))

no_poland_model_13 <- glm ( government_targets_numeric ~ 
                              age_exact +
                              is_student  + 
                              is_rural +
                              is_coal_region,
                data = filter ( eb13,
                                country_code_iso_3166!= "PL"),
                family = 'binomial')

summary (no_poland_model_13)
```

Support for the target variable `GVRNMNT TARGETS FOR RENEWABLE ENERGY` coded to binary variable (important, not important)
* is shrinking with age.
* is more likely to be supported by full-time students
* less likely to be supported in rural areas, but this is not a significant variable
* less likely to be supported in coal areas.

### Simple GLM model for Poland

The model would be similar in Poland, but the variables are not significant.

```{r simplemodelsPL, echo=TRUE}
poland_model_13 <- glm ( government_targets_numeric ~ 
                              age_exact +
                              is_student +
                              is_rural +
                              is_coal_region,
                data = filter ( eb13,
                                country_code_iso_3166 == "PL"),
                family = 'binomial')

summary(poland_model_13)
```

### Simple Model With Country Effects

One explanation for the difference is that support for the measure in Poland is overall smaller than in the EU.

```{r country13, echo=TRUE}
summary ( glm ( government_targets_numeric ~ age_exact +
                  is_student + is_rural +
                  country_code_iso_3166,
                data = eb13,
                family = 'binomial'))
```



```{r final13, echo=TRUE}
summary ( glm ( government_targets_numeric ~ age_exact +
                  is_coal_region +
                  country_code_iso_3166,
                data = eb13,
                family = 'binomial'))
```