---
title: "Processing Eurobarometer 90.2 (October-November 2018)"
author: "Daniel Antal, CFA"
date: "4/27/2020"
output: 
  github_document:
    toc: true
  html_document:
    toc: true
    theme: united
---

## Setup The Eurobarometer Package

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

list_of_packages <- installed.packages()
if ( ! "eurobarometer" %in% list_of_packages ) {
  devtools::install_github('antaldaniel/eurobarometer')
}

library(eurobarometer)
library(tidyverse)
```

## Read In Data 

You can read in the SPSS file with `haven`, which is part of `tidyverse`. 

```{r readeb18, eval=FALSE}
# Change to eval=TRUE if you want to run this code
ZA7488_raw <- haven::read_spss(file.path("not_included", "ZA7488_v1-0-0.sav"))
```

You can analyze the SPSS file with `gesis_metadata_create`.

```{r metadata, eval=FALSE}
# Change to eval=TRUE if you want to run this code
ZA7488_metadata <- gesis_metadata_create(dat = ZA7488_raw)

ZA7488 <- ZA7488_raw %>%
  purrr::set_names ( as.character(ZA7488_metadata$canonical_name)) %>%
  mutate ( region_nuts_names  = haven::as_factor(region_nuts_codes)) %>%
  mutate ( region_nuts_codes =  as.character(region_nuts_codes)) 
```

### Preprocessing the Eurobarometer 80.2 Data

```{r preprocess18, eval=FALSE}
source(file.path("R", "which_coal_region.R"))
# Change to eval=TRUE if you want to run this code
eb18 <- ZA7488 %>%
  select ( one_of("eu_env_policy_statements_more_pub_fin_support_for_clean_energy_even_if_fossil_subsidies_reduced",
                  "region_nuts_names", "region_nuts_codes",
                  "age_exact", "age_education", "type_of_community",
                  "age_education_recoded_5_cat",
                  "country_code_iso_3166", 
                  "weight_result_from_target_redressment"),
           contains("occupation")) %>%
  dplyr::rename ( eu_env_policy  = eu_env_policy_statements_more_pub_fin_support_for_clean_energy_even_if_fossil_subsidies_reduced, 
                  w1 = weight_result_from_target_redressment ) %>%
  mutate ( eu_env_policy = haven::as_factor ( eu_env_policy )) %>%
  mutate_at ( vars(starts_with("type"),
                   contains("recoded"),
                   contains("occupation")), haven::as_factor) %>%
  mutate ( eu_env_policy_numeric = case_when (
           grepl("Totally agree|Tend to agree",
                 as.character(eu_env_policy))    ~ 1,
           grepl("disagree", as.character(eu_env_policy)) ~ 0,
           TRUE ~ NA_real_ )
           ) %>%
  mutate ( is_eu_env_policy_totally = case_when (
           grepl("Totally agree",
                 as.character(eu_env_policy))    ~ 1,
           grepl("Tend to|disagree", as.character(eu_env_policy)) ~ 0,
           TRUE ~ NA_real_ )
           ) %>%
  mutate ( total_agreement_weighted = w1*is_eu_env_policy_totally) %>%
  mutate ( age_education = recode_age_education(var = age_education,
                                                age_exact = age_exact )
           ) %>%
  mutate  ( is_rural = case_when (
    grepl ( "rural", tolower(as.character(type_of_community))) ~ 1,
    grepl ( "town", tolower(as.character(type_of_community)))  ~ 0,
    tolower(as.character(type_of_community)) == "dk" ~ NA_real_,
    TRUE ~ NA_real_)
) %>%
  mutate  ( is_student = case_when (
    grepl ( "studying", tolower(as.character(age_education_recoded_5_cat))) ~ 1,
    grepl ( "refuse", tolower(as.character(type_of_community)))  ~ NA_real_,
    TRUE ~ 0)
  )  %>%
  mutate  ( is_highly_educated = case_when (
    grepl ( "20 years", tolower(as.character(age_education_recoded_5_cat))) ~ 1,
    grepl ( "refuse", tolower(as.character(type_of_community)))  ~ NA_real_,
    TRUE ~ 0)
  ) %>%
  mutate ( year_survey = 2018 ) %>%
  mutate ( coal_region = which_coal_region(region_nuts_codes)) %>%
  mutate ( is_coal_region = ifelse (is.na(coal_region), 0, 1))

saveRDS(eb18,
        file.path("data", "eb18.rds"), 
        version = 2) # backward compatiblity
```

I created a coal region proxy with this document: [Coal regions in transition](https://ec.europa.eu/energy/topics/oil-gas-and-coal/EU-coal-regions/coal-regions-transition_en)

## Simple Models 

The problem with this variable is that it has very little variance. Therefore the target variable is not `agreement` but `total agreement`.

```{r histogram}
library(ggplot2)

eb18 <- readRDS(file.path("data", "eb18.rds"))

eb18 %>%
  ggplot( data = ., 
          aes ( x= as.factor(eu_env_policy_numeric) )) +
  geom_histogram( stat = "count")


eb18 %>%
  ggplot( data = ., 
          aes ( x= as.factor(is_eu_env_policy_totally ) )) +
  geom_histogram( stat = "count")
```


### Simple GLM model outside Poland


```{r simplemodeloutsidepoland18}
summary ( glm ( is_eu_env_policy_totally ~
                  is_rural + is_highly_educated +
                  is_coal_region,
                data = filter ( eb18,
                                country_code_iso_3166!= "PL"),
                family = 'binomial'))
```

Support for the target variable `eu_env_policy_statements_more_pub_fin_support_for_clean_energy_even_if_fossil_subsidies_reduced` coded to binary variable (agree, disagree)
* is shrinking with age.
* less likely to be supported in rural areas, but this is not a significant variable
* less likely to be supported in coal areas.

### Simple GLM model for Poland

The `coal regions` in Poland are not significant and do not have a negative coefficient.

```{r simplemodelsPL18, echo=TRUE}
summary ( glm ( is_eu_env_policy_totally ~ 
                  is_rural + is_highly_educated +
                  is_coal_region,
                data = filter ( eb18,
                                country_code_iso_3166 == "PL"),
                family = 'binomial'))

```

### Simple Model With Country Effects

The Poland-only model is counterintuitive, becuase in Poland the level of total agreement is 29% less likely than in the average EU country.

```{r countrymodel18, echo=TRUE}

country_effects_18 <- glm ( is_eu_env_policy_totally ~
                              is_rural + is_highly_educated +
                              country_code_iso_3166,
                data = eb18,
                family = 'binomial')

summary ( country_effects_18 )
```

A relatively good model takes the rural regions, coal regions, high education level and countries. In Poland, even after controlling for high education level, lack of subjective urbanization and coal regions, the country effect is significantly negative.

```{r model18, echo=TRUE}
summary ( glm ( is_eu_env_policy_totally ~
                              is_rural + 
                              is_coal_region + 
                              country_code_iso_3166,
                data = eb18,
                family = 'binomial') 
          )
```