---
title: "Processing Eurobarometer 87.1 (March 2017)"
author: "Daniel Antal, CFA"
date: "4/27/2020"
output: 
  github_document:
    toc: true
  html_document:
    toc: true
    theme: united
---

## Setup The Eurobarometer Package

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

list_of_packages <- installed.packages()
if ( ! "eurobarometer" %in% list_of_packages ) {
  devtools::install_github('antaldaniel/eurobarometer')
}

library(eurobarometer)
library(tidyverse)
```

## Read In Data 

You can read in the SPSS file with `haven`, which is part of `tidyverse`. 

```{r readeb15, eval=FALSE}
# Change to eval=TRUE if you want to run this code
ZA6595_raw <- haven::read_spss(file.path("not_included", "ZA6595_v3-0-0.sav"))
```

You can analyze the SPSS file with `gesis_metadata_create`.

```{r metadata15, eval=FALSE}
# Change to eval=TRUE if you want to run this code
ZA6595_metadata <- gesis_metadata_create(dat = ZA6595_raw)

ZA6595 <- ZA6595_raw %>%
  purrr::set_names ( as.character(ZA6595_metadata$canonical_name)) %>%
  mutate ( region_nuts_names  = haven::as_factor(region_nuts_codes)) %>%
  mutate ( region_nuts_codes =  as.character(region_nuts_codes)) 
```

### Preprocessing the Eurobarometer 87.1 (March 2017) Data

```{r preprocess15, eval=FALSE}
source(file.path("R", "which_coal_region.R"))
# Change to eval=TRUE if you want to run this code
eb15 <- ZA6595 %>%
  select ( one_of("gvrnmnt_targets_for_renewable_energy_importance",
                  "region_nuts_names", "region_nuts_codes",
                  "age_exact", "age_education", "type_of_community",
                  "age_education_5_cat_recoded",
                  "country_code_iso_3166", 
                  "weight_result_from_target", 
                  "left_right_placement_3_cat_recoded"),
           contains("occupation")) %>%
  dplyr::rename ( w1 = weight_result_from_target ) %>%
   mutate ( government_targets = haven::as_factor(
    gvrnmnt_targets_for_renewable_energy_importance) ) %>%
  mutate ( government_targets_numeric =  case_when (
           grepl("Not very|Not at all", 
                 as.character(government_targets)) ~ 0,
           grepl("Fairly|Very", as.character(government_targets)) ~ 1,
           government_targets == "DK" ~ NA_real_,
           TRUE ~ NA_real_ )
           ) %>%
   mutate ( is_government_targets_totally =  case_when (
           grepl("Fairly|Not very|Not at all", 
                 as.character(government_targets)) ~ 0,
           grepl("Very", as.character(government_targets)) ~ 1,
           government_targets == "DK" ~ NA_real_,
           TRUE ~ NA_real_ )
           ) %>%
  mutate_at ( vars(starts_with("type"),
                   contains("recoded"),
                   contains("occupation")), haven::as_factor) %>%
  mutate ( total_target_agreement_weighted = w1*is_government_targets_totally) %>%
  mutate ( age_education = recode_age_education(var = age_education,
                                                age_exact = age_exact )
           ) %>%
  mutate  ( is_rural = case_when (
    grepl ( "rural", tolower(as.character(type_of_community))) ~ 1,
    grepl ( "town", tolower(as.character(type_of_community)))  ~ 0,
    tolower(as.character(type_of_community)) == "dk" ~ NA_real_,
    TRUE ~ NA_real_)
) %>%
  mutate  ( is_student = case_when (
    grepl ( "studying", tolower(as.character(age_education_5_cat_recoded))) ~ 1,
    grepl ( "refuse", tolower(as.character(type_of_community)))  ~ NA_real_,
    TRUE ~ 0)
  )  %>%
  mutate  ( is_highly_educated = case_when (
    grepl ( "20 years", tolower(as.character(age_education_5_cat_recoded))) ~ 1,
    grepl ( "refuse", tolower(as.character(type_of_community)))  ~ NA_real_,
    TRUE ~ 0)
  ) %>%
  mutate ( year_survey = 2018 ) %>%
  mutate ( coal_region = which_coal_region(region_nuts_codes)) %>%
  mutate ( is_coal_region = ifelse (is.na(coal_region), 0, 1)) %>%
  dplyr::rename ( left_right_3 =  left_right_placement_3_cat_recoded  )

saveRDS(eb15,
        file.path("data", "eb15.rds"), 
        version = 2) # backward compatiblity
```

I created a coal region proxy with this document: [Coal regions in transition](https://ec.europa.eu/energy/topics/oil-gas-and-coal/EU-coal-regions/coal-regions-transition_en)

## Simple Models 

The problem with this variable is that it has very little variance. Therefore the target variable is not `agreement` but `total agreement`.

```{r histograms}
library(ggplot2)

eb15 <- readRDS(file.path("data", "eb15.rds"))


eb15 %>%
  ggplot( data = ., 
          aes ( x= as.factor(government_targets_numeric) )) +
  geom_histogram( stat = "count")

eb15 %>%
  ggplot( data = ., 
          aes ( x= as.factor(is_government_targets_totally) )) +
  geom_histogram( stat = "count")

```


### Simple GLM model outside Poland


```{r simplemodeloutsidepoland15b}
summary ( glm ( is_government_targets_totally  ~
                  age_exact + 
                  is_highly_educated +
                  is_coal_region + left_right_3,
                data = filter ( eb15,
                                country_code_iso_3166!= "PL"),
                family = 'binomial'))
```

Support for the target variable `transition_policy_statements_more_pub_fin_support_for_clean_energy_even_if_fossil_subsidies_reduced` coded to binary variable (agree, disagree)
* is shrinking with age.
* less likely to be supported in rural areas, but this is not a significant variable
* less likely to be supported in coal areas.

### Simple GLM model for Poland

The `coal regions` in Poland are not significant and do not have a negative coefficient.

```{r simplemodelsPL15b, echo=TRUE}
summary ( glm ( is_government_targets_totally ~ 
                  age_exact +
                  is_highly_educated +
                  is_coal_region +left_right_3,
                data = filter ( eb15,
                                country_code_iso_3166 == "PL"),
                family = 'binomial'))

```

### Simple Model With Country Effects

The Poland-only model is counterintuitive, becuase in Poland the level of total agreement is 35% less likely than in the average EU country.


```{r countrymodel15b, echo=TRUE}

country_effects_18 <- glm ( is_government_targets_totally ~
                              age_exact + is_highly_educated +
                              left_right_3 +
                              country_code_iso_3166,
                data = eb15,
                family = 'binomial')

summary ( country_effects_18 )
```

A relatively good model takes the rural regions, left-right self-placement, high education level and countries. In Poland, even after controlling for high education level, lack of subjective urbanization and left-right placement, the country effect is significantly negative.

The coal region effect becomes less significant if we add left-right self-placement and reletive education level. Those, who do not support the climate targets tend to be rigth-wing, rural people who are more concentrated in the coal areas. 

```{r model15b, echo=TRUE}
summary ( glm ( is_government_targets_totally  ~
                    left_right_3 +
                    is_coal_region + 
                    is_highly_educated +
                    country_code_iso_3166,
                data = eb15,
                family = 'binomial') 
          )
```