---
title: "Simple Analysis Of Policy Agreement & Air Pollutants"
author: "Daniel Antal, CFA"
date: "5/5/2020"
output: 
  github_document:
    toc: true
  html_document:
    toc: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(fastDummies)
library(factoextra)
library(tibble)
library(stringr)
eb19_raw <- readRDS( "data/eb19.rds") 
normalize_text <- function(x) {
  
  x <- as.character(x)
  x <- tolower(x)
  x <- str_trim(x, side = "both")
  x <- gsub("\\s", "_", x)
  x <- gsub(":|!|,|;|%","", x)
  x <- gsub("____|___|__", "_", x)
  x
}

#source("R/air_pollutants.R")
load("data/air_pollutants.rda")
```

## Data Preparation


```{r dataprep}
transition_policy <- eb19_raw %>%
  rowid_to_column() %>%
  mutate ( transition_policy = normalize_text(transition_policy)) %>%
  fastDummies::dummy_cols(select_columns = 'transition_policy') %>%
  mutate ( transition_policy_agree = case_when(
    transition_policy_totally_agree + transition_policy_tend_to_agree > 0 ~ 1, 
    TRUE ~ 0
  )) %>%
  mutate ( transition_policy_disagree = case_when(
    transition_policy_totally_disagree + transition_policy_tend_to_disagree > 0 ~ 1, 
    TRUE ~ 0
  )) 
```


## PCA

If later needed, calculate the principal components:

```{r pca, echo=FALSE}
transition_policy_pca <- prcomp(transition_policy [,c(25:29)], scale = TRUE)
fviz_eig(transition_policy_pca)

transition_policy <- transition_policy  %>%
  bind_cols( 
    transition_policy_pca$x %>%
      as_tibble() %>%
      purrr::set_names ( ., paste0("tp_", tolower(names(.))))
  )
```

```{r pollutants}
eb19_df  <- transition_policy %>% 
  left_join ( air_pollutants, by = 'region_nuts_codes' ) %>%
  mutate ( is_poland = ifelse ( country_code == "PL", 1, 0))
```


## Agreement 

Significantly more people agree where
- there are more polutants
- who are younger
- more educated
- in many countries, including from V4 Hungary

Significantly less people agree 
- in rural areas
- older
- less educated
- less polluted
- coal regions 
- Belgium (coal), Bulgaria, Croatia, Czechia, Estonia, Italy, Lativa, Luxembourg (coal), Finland, Poland, Romania, Slovakia


```{r agreement}
c("transition_policy_totally_agree" , "pm10", "so2", "age_exact", "is_highly_educated" , "is_rural")

summary( glm ( transition_policy_totally_agree ~ pm10 + so2 + 
                 age_exact +
                 is_highly_educated + is_rural + is_coal_region +
                 country_code, 
               data = eb19_df, 
               family = binomial ))

summary( glm ( transition_policy_agree ~ pm10 + so2 + age_exact +
                 is_highly_educated + is_rural, 
               data = eb19_df, 
               family = binomial ))
```

## Disagreement

The disagreement is consistent with the agreement variables.

Explicit disagreement is higher when 
- there is coal
- less pollutants

Polish people are significantly less likely to agree. Disagreement is more difficult to model, because the vast majority of the people tend to agree.


```{r disagreement}
summary( glm ( transition_policy_totally_disagree ~ 
                 pm10 + so2  + is_coal_region,  
               data = eb19_df,
               family = binomial ))

summary( glm ( transition_policy_disagree ~ pm10 + so2 + is_coal_region +
                 is_poland, 
               data = eb19_df, 
               family = binomial ))
```

```{r models}
```